\chapter*{Abstract}


Real-time processing of data is of utmost importance in embedded systems since the micro-computing device present in the embedded system handles a tremendous amount of data coming from environmental events and internal events. 
The current trending micro-computing device in embedded systems is a lightweight high-performance system on a chip. 
This system on a chip, along with the microcomputer environments contains smart power devices for providing diagnostic and protection features. 

At Kompetenzzentrum fur Automobil- und Industrieelektronik GmbH there exists a reliability test system concept for testing of semiconductor power devices called Modular Power Stress test architecture~\cite{Steinwender2016}.
The performance of the reliability test during the design of semiconductor power devices and its system plays a vital role as in real-world, semiconductor devices are subjected to numerous stresses.
These stresses are electrical stress, mechanical stress or thermal stress. 
In response to the mentioned stresses, several electrical signals need to be measured in the semiconductor device.
Measurement and interpretation of these electrical signals are performed using a microcontroller in the Modular Power Stress test architecture. 
The Microcontroller acts as a controlling and measuring agent of the stress that is undergone by the semiconductor power devices.
To measure the analog signals, the microcontroller makes use of a data processing mechanism.  
In this work, high-speed analog measurement processing concepts for a microcontroller are delivered and processing of analog measurements is automated irrespective of the type of stress tests that are performed. 

\vspace{1cm}
